Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-10 paper.tex
Typo in heading 'Internal Processing and Communication'

\subsubsection{Internal processing and Communication}
Another critical aspect directly related to performance and responsiveness
is how data is internally processed, stored, and communicated.
This includes metadata collected and processed
and involves data exchange with all relevant backend services or instances.

>>>>

\subsubsection{Internal Processing and Communication}
Another critical aspect directly related to performance and responsiveness
is how data is internally processed, stored, and communicated.
This includes metadata collected and processed
and involves data exchange with all relevant backend services or instances.
